\vspace{-2.0cm}Stuff

### 2014-05-13 report/draft.tex
Completed: Half normal & Emperical detection functions. Completed: Detected Functions Working On: Density Estimates.

@@

>>>>

Ramsey 1979
Uniform distribution, random process distribution, independent distribution,

@@

\section{Simulation Setup}
\subsection{$g(0)$}
\subsubsection{Half Normal}
For a maximum possible observation distance of 0.500 (500 m), the parameter for the half-normal detection function is $\theta = 8.77$, with a scale parameter $\delta = 0.179$.

The half-normal parameter $\theta$ is related to the standard deviation of a standard normal distribution by the relationship:

$\theta = \frac{\sqrt{\pi /2}}{\sigma}$

If we estimate $\sigma$ by $w/3.5$ (with $w$ being the maximum distance at which we might observe an object, and 3.5 being the standard deviation point where P(X > 3.5) < 0.001) then theta is:

$\sigma = w/3.5 = 0.1429$

$\theta = \frac{\sqrt{\pi /2}}{0.1429}=8.7732$

For a half-normal with parameter $\theta=8.7732$, $f(0)=5.5852$ so to scale the value to 1:

$\delta_{HN} = 1/5.5852 = 0.1790$

\subsubsection{Empirical Observations}
\begin{figure}

	\includegraphics[width=\textwidth]{../images/loess.pdf}
	\caption{Empirical Observation Distances from Original data in meters, with LOESS regression lines. Bin width=5 m\label{fig:by5}}

\end{figure}

We can see in Figure \ref{fig:by5} that above 100 m, observations were commonly heaped into 10 or 25 m distances, with the latter being more heavily used. Above 200 m, 50 m heaps were common. To estimate a density function, I used a loess regression with a span of 0.2 on the counts from 5 meter bins of the empirical data. This is the blue line in Figure \ref{fig:by5}.

Using the \texttt{hist()} function in R, the 1982 observation distances were broken into counts by 5 m groups. Using the bin midpoints, the density estimate was multiplied by 5 to get the density value for that bin. A LOESS regression was run with the midpoint as $x$ and $y=density*5$, using the \texttt{loess()} package in R.

This gives us an object that can be used with \texttt{predict()} to get density estimates for specific distances. The values generated by feeding our midpoints into our prediction function are represented by the red dashed line in Figure \ref{fig:by5}.

Following the scaling of the highest point to 1, as was done with the half normal curve, where the highest point was $g(0)$, we also find $\delta$ for this empirical detection probability. A sequence of $x$ values was generated covering the range from 0--500 m. This was plugged into the \texttt{predict()} function using our LOESS object. The highest density value was then scaled to be 1:

$\delta_{EMP}=\frac{1}{max(predicted)}=40.5780$
